The Magnetorotational Instability Prefers Three Dimensions

### 2019-11-11 paper/paper.tex
i've checked it as well as i can at this point.

Finally, we can continue with the calculation conceptually. Because of symmetry $\gamma_{3}(\s,\x) = 0$ identically. This means that to leading order 
\Beq
\gamma(\s,k_{y},k_{z}) \ = \ \gamma_{0}(\s,\x) + \gamma_{2}(\s,\x) k_{y}^{2}  + \gamma_{4}(\s,\x) k_{y}^{4} \ + \ \ldots
\Eeq 
For $\SSC > S_{2D}/S_{c}$, $\gamma_{2} > 0$. This is sufficient to determine the most unstable 3D wavenumber near the transition to dominant 2D modes, 
\Beq
k_{y}^{2} \ \approx \ -\frac{\gamma _2}{2 \gamma_4} \ \propto \  S_{2D}/S_{c} - \SSC . 
\Eeq 
Generically $\gamma_{4} \ne 0$. We assume that $\gamma_{4} < 0$, but we do not know for sure if this is the case. The calculation is considerably more challenging that what we already have done. If there is a negative 4th-order feedback, then 
\Beq
k_{y} \ \sim \ \sqrt{S_{2D}/S_{c} - \SSC}. 
\Eeq
This is consistent with Figure~\ref{fig:growth_rate}d near the critical point. If $\gamma_{4} > 0$, then the calculation would proceeded to 6th order (and so on), and the critical exponent will be smaller. Nevertheless the general picture will stay the same.

>>>>

Finally, we can continue with the calculation conceptually. Because of symmetry $\gamma_{3}(\s,\x) = 0$ identically. This means that to leading order 
\Beq
\gamma(\s,k_{y},k_{z}) \ = \ \gamma_{0}(\s,\x) + \gamma_{2}(\s,\x) k_{y}^{2}  + \gamma_{4}(\s,\x) k_{y}^{4} \ + \ \ldots
\Eeq 
For $\SSC > S_{2D}/S_{c}$, $\gamma_{2} > 0$. This is sufficient to determine the most unstable 3D wavenumber near the transition to dominant 2D modes, 
\Beq
k_{y}^{2} \ \approx \ -\frac{\gamma _2}{2 \gamma_4} \  \propto \   S_{2D}/S_{c} - \SSC   . 
\Eeq 
Generically $\gamma_{4} \ne 0$. We assume that $\gamma_{4} < 0$, but we do not know for sure if this is the case. The calculation is considerably more challenging than anything so far. If there is a negative 4th-order feedback, then 
\Beq
k_{y} \ \sim \ \sqrt{S_{2D}/S_{c} - \SSC}, 
\Eeq
which is consistent with Figure~\ref{fig:growth_rate}d near the critical point. Furthermore, a scenario where $\gamma_{4} > 0$ would require behaviour that is inconsistent with Figure~\ref{fig:growth_rate}d.
